Staged Abstract Interpreters

### 2018-11-04 paper/20_bg.tex
write about LMS in section 2.3.1

>>>>

Lightweight modular staging (LMS) \todo{cite} is a library-based multi-stage programming framework 
that enables type-safe dynamic code generation. Different from the traditional approach of using
syntactic quasi-quotation, it solely relies on types to distinguish between binding times.

In the example shown above, \texttt{power} is a staged function that takes 2 arguments where 
\texttt{b} is declared as \texttt{Rep[Int]} meaning that \texttt{b} is a representation of type 
\texttt{Int} whose underlying value will be available at the next stage. Meanwhile the actual 
computation result of the \texttt{power} function  will be available at the next stage as well. 
Thus the return value of \texttt{power} is also of type \texttt{Rep[Int]}. The generated code for
\texttt{power5} consists of a function that takes only one argument that corresponds to its 
representation \texttt{b} from the previous stage.
